OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-02 paper/paper.Rmd
Report sampling methods results at reffrac 0.5

**TODO: pick a fraction (e.g. 50%). this part is less important. figure would be supplemental.**
After testing the split strategy using a simple random sample to select the reference sequences, we then investigated other methods of splitting the data.
We tested three methods for selecting the fraction of sequences to be used
as the reference; a simple random sample, weighting sequences by relative
abundance, and weighting by similarity to other sequences in the dataset.
OTU quality was similar with the simple and abundance-weighted sampling (median
MCCs `r mcc_fit_split_simple` and `r mcc_fit_split_abun` respectively), but
worse for similarity-weighted sampling with a median MCC of `r mcc_fit_split_dist`.
In closed reference mode, the fraction of query sequences that can be fit to the
reference OTUs increases as the reference fraction increases; from 
`r frac_fit_split_1`% of query sequences fit when using 10% of the dataset as 
the reference, to `r frac_fit_split_9`% of query sequences fit when using 90% 
of the dataset as the reference. **TODO: report up to 90% fraction**

>>>>

After testing the split strategy using a simple random sample to select the
reference sequences, we then investigated other methods of splitting the data.
We tested three methods for selecting the fraction of sequences to be used as
the reference at a size of 50%; a simple random sample, weighting sequences by
relative abundance, and weighting by similarity to other sequences in the
dataset.
OTU quality in terms of MCC was similar with the simple and abundance-weighted
sampling (median MCCs of `r mcc_fit_split_simple` and `r mcc_fit_split_abun`
respectively), but worse for similarity-weighted sampling (median MCC of
`r mcc_fit_split_dist`).
In closed-reference clustering mode, the fraction of sequences that mapped were
similar for simple and abundance-weighted sampling (median fraction mapped of 
`r frac_fit_split_simple` and `r frac_fit_split_abun` respectively), but worse 
for similarity-weighted sampling (median fraction mapped of `r frac_fit_split_dist`).
While simple and abundance-weighted sampling produced better quality OTUs than
similarity-weighted sampling, OptiFit performed faster on
similarity-weighted samples with a median runtime of `r sec_fit_split_dist`
seconds compared to `r sec_fit_split_simple` and `r sec_fit_split_abun` seconds
for simple and abundance-weighted sampling (respectively).
Thus, employing more complicated sampling strategies such as abundance-weighted
and similarity-weighted sampling did not confer any advantages over selecting
the reference via a simple random sample, and in fact decreased OTU quality in
the case of similarity-weighted sampling.
